How to Name a Real-World Object, and how not to

### 2019-12-06 papers/ACL2020/experiments.tex
[ACL2020] more in experiments.tex

\paragraph{Models}
We test two object detection models that are trained with a different vocabulary:

>>>>

\paragraph{Models}
We test two object detection models which both use the Faster R-CNN architecture \cite{fasterrcnn2015}, and were initialized with features that were pre-trained on $1K$~ImageNet classes with the ResNet-101 classification model \cite{he2016deep}. 
They were both trained on \vg, but, essentially, differ in their target vocabulary. 
FRCNN--VG1600\footnote{We used the code and model of \citeauthor{anderson2018updown}'s \shortcite{anderson2018updown} bottom-up attention model, available at  \url{github.com/peteanderson80/bottom-up-attention}. The model is trained with an additional output over attributes, but we only use the object class prediction layer.} \cite{anderson2018updown} uses a vocabulary of $1600$~object classes \cs{add how it was derived}.
For FRCNN--MN442, we pre-process the \vg data as in \citeauthor{anderson2018updown} \cs{right, @Sina?}, but restrict the object classes to the $442$~entry-level names found in \mn (Section~\ref{sect:?}). 
For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}

Using transfer learning, we further test a range of Vanilla object classification models consisting of multi-layer neural networks.  
To predict the entry-level name of a target object, they are fed image features extracted for the target's bounding box, and apply softmax at the output layer that corresponds to the vocabulary of target names. 
The models differ in the pre-trained image features used for feature extraction, in the training signal, and, similarly to the FRCNN models above, in the vocabulary that we use for training them: 
Regarding the features, we either use the FRCNN--VG1600 model above (i.e.,~the features were pre-trained on \vg), or use the ResNet-101 model that was used to initialize the FRCNN models above. 
Note that ResNet's $1K$~object classes capture subordinate categories of ImageNet leaf nodes (e.g.,~Siberian husky, American black bear). 
Vocab + signal:

### 2019-12-06 papers/ACL2020/introduction.tex
[ACL2020] starts filling in experiments.tex
[ACL2020] more in experiments.tex

\cs{need to make clear the diff btw objects meaning the concept/class and meaning an instance}

@@

Despite its relevance in \lv, the challenge of instance-based natural naming has been overseen, and most \lv datasets not necessarily provide enough information to make progress on the problem of modeling natural object naming (they only provide very few names). 
Research that particularly focuses on the prediction of entry-level names is scarce, and existing work has adopted (i) taxonomic view (?) and (ii) developed specialized methods implementing the taxonomic view (?)\cite{Ordonez:2016}. \cs{check paper}
%
\begin{figure}
	\centering
	\small
	\begin{tabular}{p{3cm}p{3cm}}
		%VisualGenome+ManyNames & \cite{snodgrass}\\
		\centering
		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
	\end{tabular}

>>>>

\cs{need to make clear the diff btw objects meaning the concept/class and meaning an instance}
\cs{need to discuss problematic of standard evaluation procedure of CV models}

@@

Despite its relevance in \lv, the challenge of instance-based natural naming has been overseen, and most \lv datasets not necessarily provide enough information to make progress on the problem of modeling natural object naming (they only provide very few names). 
Research that particularly focuses on the prediction of entry-level names is scarce, and existing work has adopted the view that (i) entry-level names arise on the conceptual level, and (ii) developed specialized methods \cite{Ordonez:2016}. 
%To our knowledge, work that gives systematic insights into the ability of standard object recognition models to account for natural object naming, and in how far simple \cs{straightfoward?} re-training or transfer learning can increase this ability, is lacking. 
%
\begin{figure}
	\centering
	\small
	\begin{tabular}{p{3cm}p{3cm}}
		%VisualGenome+ManyNames & \cite{snodgrass}\\
		\centering
		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
	\end{tabular}
